Leadership across cultures and contexts: an exploratory analysis

### 2020-05-11 leadership_across_cultures_contexts.Rmd
Adding text to SI.

@@

>>>>

The 60-culture Probability Sample Files of the HRAF developed by @naroll_proposed_1967 is based on culturally and geographically diverse populations which are well covered in the ethnographic record. The distribution of cultures, however, is not equal across categories of subsistence strategies; agriculturalists and horticulturalists are relatively overpresented compared to hunter-gatherers and pastoralists. The ethnographic sample of text developed in the *leadershipdata* package is also not equally balanced across all subsistence stragey categories. See Figure S\@ref(fig:subsisttree).

@@

The distribution of cultures by subsistence stragegy across conteinetla region is also variable. In this sample, most African cultures are agriculturalists and most North American cultures are hunter-gatherers, for example. See Figure S\@ref(fig:regionsubsistence).
